Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-18 main.Rmd
normalise new results

### Estimating distributions

@@

#### Distribution of Jensen-Shannon distances

Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values. Taking sample percentiles to approximate the integral would mean taking $m = 99$.
With large $m$, chi-squared is asymptotically normal by the CLT. Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution. Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made.

>>>>

### Characterising distribution

@@

<!-- #### Distribution of Jensen-Shannon distances -->

<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values. Taking sample percentiles to approximate the integral would mean taking $m = 99$. -->
<!-- With large $m$, chi-squared is asymptotically normal by the CLT. Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution. Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made. -->

### Distance measure

The algorithm employed for computing the distance measure is summarized as follows:

5. Compute maximum distance ($M$) using appropriate norming constants.

6. Use Steps 1-5 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.

7. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.

However, median and maximum distances are not robust to the number of levels and the distance measure MMPD_raw would have higher values if $C_i$ or $C_j$ has higher levels. Figure \ref{fig:mean-sd-max} shows how distribution of MMPD_raw varies for different levels of $C_i$ and $C_j$. In this example, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 3, 4, 5,7 ,9, 14, 21, 30, 45)$. Each of these combinations is considered a panel for each of which MMPD_raw has been constructed 100 times to compute the distribution. This shows that with the increase in the number of levels of $C_i$, the distributions shift rightward and upward. With increasing number of levels of x-axis, such a direction is not clear. This implies we need to atleast normalise for the levels of the facets so that we could correctly compare MMPD_raw across different combinations.

both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$). There is a rightward shift in the location and decrease in scale with increasing $n$.

Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies. The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
